Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-22 Manuscript/FLPhish(Trans).tex
修改Models and Design Goals

\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($c_{i}$ indicates the $i$th client in FL) keeps the local dataset $d_{i}$ collected by itself. FL client $c_{i}$ uses its local dataset $d_{i}$ to update the model received from the FL server. Then it dispatches the gradient updates of the model back to the FL server. Meanwhile, it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.

\subsection{Threat Model}
The current system still suffers from the Byzantine attacks. Malicious Byzantine client $b$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $b$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}. Byzantine client $b$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $b$ dispatches the false updates of the gradient to the central server. Therefore the false updates of the gradient cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size value larger than $d_{i}$'s real size value. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

@@

\par \textit{1)} Inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
\par \textit{2)} Our proposed Ensemble FL architecture lacks protection against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based model to guard against Byzantine attacks in our proposed Ensemble FL system.
\par \textit{3)} To accurately assess clients' behaviors, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

>>>>

\subsubsection{{FL Client}} Each FL client {$c_{i}$} ($c_{i}$ indicates the $i$th client in FL) keeps the local dataset $d_{i}$ collected by itself. FL client $c_{i}$ uses its local dataset $d_{i}$ to update the model received from the FL server. Then it dispatches the model gradient updates back to the FL server. Meanwhile, it repeats the above actions in the whole process of FL until the FL server $s$ stops sending the new model.

\subsection{Threat Model}
The current system still suffers from the Byzantine attacks. Malicious Byzantine client $c_{i}$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $c_{i}$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}. Byzantine client $c_{i}$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $c_{i}$ dispatches the false model gradient updates to the central server. Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

@@

\par \textit{1)} Typical FL architecture has many drawbacks including not being compatible with different deep learning models in different clients and high communication cost. Thus, inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provides more opportunities for us to counter Byzantine attacks in FL.
\par \textit{2)} The proposed Ensemble FL architecture still lacks effective protection mechanism against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based mechanism to guard against Byzantine attacks in our proposed Ensemble FL system.
\par \textit{3)} As the performance of each client will not remain stable in each iteration, it is important for our scheme to accurately measure each client's level of confidence in a long term. Therefore, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
\par \textit{4)} With each client's level of confidence measured accurately via reputation mechanism, the aggregation rule of the Ensemble FL architecture should be reconsidered on the basis of each client's reputation. Furthermore, we propose two aggregation rules in FLPhish, FLPhish-threshold, and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.
